MonteCarlo Simulation's of the Covid-19 Pandemic

### 2022-12-15 paper.rmd
update\n

# recreate plots
positive <- ggplot(data = china) +
  geom_point(aes(x = date, y = total_cases)) +
  theme(title =element_text(size=6)) +
  labs(title = "Figure 1: Total Cases in China from 1/22/2020 to 3/27/2020",
       x = "Date", y = "China cumulative number of cases")
positive

ggplot(data = china) +
  geom_point(aes(x = date, y = total_deaths)) +
  theme(title =element_text(size=6)) +
  labs(title = "Figure 2: Total Deaths in China from 1/22/2020 to 3/27/2020",
       x = "Date", y = "China cumulative number of fatalities") +
  ylim(0,5000)
```

@@

```{r, results=FALSE, echo=FALSE, message=FALSE, warning=FALSE}
gauss_fn <- function(x,a,b,c,d) {a+b*erf(c*x-d)}
model1 <- nls(total_cases ~ gauss_fn(days,a,b,c,d), data=china, start=list(a=10000,b=10000,c=0.1,d=1))
# summary(model1)$parameters
fn_model1 <- function(x) {4.017e+04 + 4.047e+04 * erf(9.284e-02 * x - 1.732e+00)}
ggplot(data = china) +
  geom_point(aes(x = days, y = total_cases)) +
  theme(title =element_text(size=6)) +
  labs(title = "Figure 3: Total Cases in China with Gauss Error Function",
       x = "Days", y = "China cumulative number of cases") +
  stat_function(fun=fn_model1, color="#d33636", size=1.5)

@@

model2 <- nls(total_deaths ~ gauss_fn(days,a,b,c,d), data=china, start=list(a=10000,b=10000,c=0.1,d=1))
#summary(model2)$parameters
fn_model2 <- function(x) {1.571e+03 + 1.658e+03 * erf(6.194e-02 * x - 1.533e+00)}
ggplot(data = china) +
  geom_point(aes(x = days, y = total_deaths)) +
  theme(title =element_text(size=6)) +
  labs(title = "Figure 4: Total Deaths in China with Gauss Error Function",
       x = "Days", y = "China cumulative number of fatalities") +
  ylim(0,5000) +
  stat_function(fun=fn_model2, color="#1b95ff", size=1.5)
```

@@

#plot
ggplot(italy, aes(x = days, y = total_cases)) + 
    geom_point() + 
    theme(title =element_text(size=6)) +
    labs(title = "Figure I: Total Cases in Italy from 2/15/2020 to 3/29/2020", x = "Days", y = "Total Cases")
#plot
ggplot(italy, aes(x = days, y = total_deaths)) +
    geom_point() + 
    theme(title =element_text(size=6)) +
    labs(title = "Figure II: Total Deaths in Italy from 2/15/2020 to 3/29/2020", x = "Days", y = "Total Deaths")
```

@@

#plot
ggplot(italy, aes(x = days, y = total_cases)) + 
    geom_point() + 
    stat_function(fun=cf_italy, color="#d33636", size=1.5, linetype="solid") +
    scale_x_continuous(breaks = seq(0, 67, 10)) +
    theme(title =element_text(size=6)) +
    labs(title = "Figure III: Total Cases in Italy from 2/15/2020 to 3/29/2020", x = "Days", y = "Total Cases")
#plot
ggplot(italy, aes(x = days, y = total_deaths)) +
    geom_point() + 
    stat_function(fun=df_italy, color="#1b95ff", size=1.5, linetype="solid") +
    scale_x_continuous(breaks = seq(0, 67, 10)) +
    theme(title =element_text(size=6)) +
    labs(title = "Figure IV: Total Deaths in Italy from 2/15/2020 to 3/29/2020", x = "Days", y = "Total Deaths")
```

@@

```{r, results=FALSE, echo=FALSE, message=FALSE, warning=FALSE}
ggplot() +
    geom_point(aes(x=1:m, y=flex_ca), color="#d33636") +
    geom_hline(yintercept=mean(flex_ca), color="#d33636", linetype="dashed", size=1.5) + 
    theme(title =element_text(size=6)) +
    labs(title = "Figure V: Scatter Plot of MC Cases Day of Flex (Italy)", x = "Trial", y = "Day of Flex")
#plot(cs)
ggplot(italy, aes(x = days, y = total_cases)) + 
    geom_point() + 
    stat_function(fun=cf_italy, color="#d33636", size=1.5, linetype="solid") +
    scale_x_continuous(breaks = seq(0, 67, 10)) +
    theme(title =element_text(size=6)) +
    labs(title = "Figure VI: Total Cases in Italy from 2/15/2020 to 3/29/2020", x = "Days", y = "Total Cases") + 
  geom_vline(xintercept = mean(flex_ca), color="#d33636", size=1, linetype="dashed")
```

@@

```{r, results=FALSE, echo=FALSE, message=FALSE, warning=FALSE}
ggplot() +
    geom_point(aes(x=1:146, y=flex_fa), color="#1b95ff") +
    geom_hline(yintercept=mean(flex_fa), color="#1b95ff", linetype="dashed", size=1.5) + 
    theme(title =element_text(size=6)) +
    labs(title = "Figure VII: Scatter Plot of MC Fatality Day of Flex (Italy)", x = "Trial", y = "Day of Flex")
#plot(ft)
ggplot(italy, aes(x = days, y = total_deaths)) +
    geom_point() +
    stat_function(fun=df_italy, color="#1b95ff", size=1.5, linetype="solid") +
    scale_x_continuous(breaks = seq(0, 67, 10)) +
    theme(title =element_text(size=6)) +
    labs(title = "Figure VIII: Total Deaths in Italy from 2/15/2020 to 3/29/2020", x = "Days", y = "Total Deaths") +
  geom_vline(xintercept = mean(flex_fa), color="#1b95ff", size=1, linetype="dashed")
```

>>>>

# recreate plots
positive <- ggplot(data = china) +
  geom_point(aes(x = date, y = total_cases)) +
  theme(title =element_text(size=6)) +
  labs(title = "Figure 1: Total Cases in China from 1/22/2020 \nto 3/27/2020",
       x = "Date", y = "China cumulative number of cases")
positive

ggplot(data = china) +
  geom_point(aes(x = date, y = total_deaths)) +
  theme(title =element_text(size=6)) +
  labs(title = "Figure 2: Total Deaths in China from 1/22/2020 \nto 3/27/2020",
       x = "Date", y = "China cumulative number of fatalities") +
  ylim(0,5000)
```

@@

```{r, results=FALSE, echo=FALSE, message=FALSE, warning=FALSE}
gauss_fn <- function(x,a,b,c,d) {a+b*erf(c*x-d)}
model1 <- nls(total_cases ~ gauss_fn(days,a,b,c,d), data=china, start=list(a=10000,b=10000,c=0.1,d=1))
# summary(model1)$parameters
fn_model1 <- function(x) {4.017e+04 + 4.047e+04 * erf(9.284e-02 * x - 1.732e+00)}
ggplot(data = china) +
  geom_point(aes(x = days, y = total_cases)) +
  theme(title =element_text(size=6)) +
  labs(title = "Figure 3: Total Cases in China with \nGauss Error Function",
       x = "Days", y = "China cumulative number of cases") +
  stat_function(fun=fn_model1, color="#d33636", size=1.5)

@@

model2 <- nls(total_deaths ~ gauss_fn(days,a,b,c,d), data=china, start=list(a=10000,b=10000,c=0.1,d=1))
#summary(model2)$parameters
fn_model2 <- function(x) {1.571e+03 + 1.658e+03 * erf(6.194e-02 * x - 1.533e+00)}
ggplot(data = china) +
  geom_point(aes(x = days, y = total_deaths)) +
  theme(title =element_text(size=6)) +
  labs(title = "Figure 4: Total Deaths in China with \nGauss Error Function",
       x = "Days", y = "China cumulative number of fatalities") +
  ylim(0,5000) +
  stat_function(fun=fn_model2, color="#1b95ff", size=1.5)
```

@@

#plot
ggplot(italy, aes(x = days, y = total_cases)) + 
    geom_point() + 
    theme(title =element_text(size=6)) +
    labs(title = "Figure I: Total Cases in Italy from 2/15/2020 \nto 3/29/2020", x = "Days", y = "Total Cases")
#plot
ggplot(italy, aes(x = days, y = total_deaths)) +
    geom_point() + 
    theme(title =element_text(size=6)) +
    labs(title = "Figure II: Total Deaths in Italy from 2/15/2020 \nto 3/29/2020", x = "Days", y = "Total Deaths")
```

@@

#plot
ggplot(italy, aes(x = days, y = total_cases)) + 
    geom_point() + 
    stat_function(fun=cf_italy, color="#d33636", size=1.5, linetype="solid") +
    scale_x_continuous(breaks = seq(0, 67, 10)) +
    theme(title =element_text(size=6)) +
    labs(title = "Figure III: Total Cases in Italy from 2/15/2020 \nto 3/29/2020", x = "Days", y = "Total Cases")
#plot
ggplot(italy, aes(x = days, y = total_deaths)) +
    geom_point() + 
    stat_function(fun=df_italy, color="#1b95ff", size=1.5, linetype="solid") +
    scale_x_continuous(breaks = seq(0, 67, 10)) +
    theme(title =element_text(size=6)) +
    labs(title = "Figure IV: Total Deaths in Italy from 2/15/2020 \nto 3/29/2020", x = "Days", y = "Total Deaths")
```

@@

```{r, results=FALSE, echo=FALSE, message=FALSE, warning=FALSE}
ggplot() +
    geom_point(aes(x=1:m, y=flex_ca), color="#d33636") +
    geom_hline(yintercept=mean(flex_ca), color="#d33636", linetype="dashed", size=1.5) + 
    theme(title =element_text(size=6)) +
    labs(title = "Figure V: Scatter Plot of MC Cases Day of Flex (Italy)", x = "Trial", y = "Day of Flex")
#plot(cs)
ggplot(italy, aes(x = days, y = total_cases)) + 
    geom_point() + 
    stat_function(fun=cf_italy, color="#d33636", size=1.5, linetype="solid") +
    scale_x_continuous(breaks = seq(0, 67, 10)) +
    theme(title =element_text(size=6)) +
    labs(title = "Figure VI: Total Cases in Italy from 2/15/2020 \nto 3/29/2020", x = "Days", y = "Total Cases") + 
  geom_vline(xintercept = mean(flex_ca), color="#d33636", size=1, linetype="dashed")
```

@@

```{r, results=FALSE, echo=FALSE, message=FALSE, warning=FALSE}
ggplot() +
    geom_point(aes(x=1:146, y=flex_fa), color="#1b95ff") +
    geom_hline(yintercept=mean(flex_fa), color="#1b95ff", linetype="dashed", size=1.5) + 
    theme(title =element_text(size=6)) +
    labs(title = "Figure VII: Scatter Plot of MC Fatality Day of Flex (Italy)", x = "Trial", y = "Day of Flex")
#plot(ft)
ggplot(italy, aes(x = days, y = total_deaths)) +
    geom_point() +
    stat_function(fun=df_italy, color="#1b95ff", size=1.5, linetype="solid") +
    scale_x_continuous(breaks = seq(0, 67, 10)) +
    theme(title =element_text(size=6)) +
    labs(title = "Figure VIII: Total Deaths in Italy from 2/15/2020 \nto 3/29/2020", x = "Days", y = "Total Deaths") +
  geom_vline(xintercept = mean(flex_fa), color="#1b95ff", size=1, linetype="dashed")
```
